Analyzing Coopetition Strategies of Services within Communities

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

In this section, we provide an empirical analysis over the
observed results regarding the characteristics of intelligent web
services hosted in different communities of web services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, web services as service providers, and
master web services as community representatives. These entities
are developed with respect to what is explained in Section
\ref{Preliminaries}. The objective is to investigate the
effectiveness of the proposed strategic system on intelligent
web services' overall budge and also the average quality and quantity of tasks performed by 
community web services which directly affects user satisfaction. 
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
We study the overall performance of the community hosting the
reasoning-empowered web services compared to the ones hosting
stochastic and purely competitive services. The simulation
application is written in \textit{C\#} using \textit{Visual Studio}. 
Developed web services are initialized with values taken
from a real dataset that includes $2507$ real web services
functioning on the web. The dataset records the QoS values of $9$
parameters including \textit{availability}, \textit{throughput},
and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

@@

In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low. For any reason our web services may need to stay in a particular comuunity with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have inceased the membership fee to the high ammount of 5 per run. Web services will need to pay 5 bucks on each iteration of tasks being offered. As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities. As reseults show the random and all compete strategies make webservices bank deplete in no time. However our strategic coopetetive decision making process loses budget in a slower pace.

@@

hihi

>>>>

In this section, we provide an empirical analysis over the
observed results regarding the characteristics of intelligent web
services hosted in different communities of web services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, web services as service providers, and
master web services as community representatives. These entities
are developed with respect to what is explained in Section
\ref{Preliminaries}. The objective is to investigate the
effectiveness of the proposed strategic system on intelligent
web services' overall budge and also the average QoS of tasks performed by 
community web services which directly affects user satisfaction. 
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
We study the overall performance of the community hosting the
reasoning-empowered web services compared to the ones hosting
stochastic and purely competitive services. The simulation
application is written in \textit{C\#} using \textit{Visual Studio}. 
Developed web services are initialized with values taken
from a real dataset that includes $2507$ real web services
functioning on the web. The dataset records the QoS values of $9$
parameters including \textit{availability}, \textit{throughput},
and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

@@

@@
